### 2020-06-13 chapters/sota.tex
...

\subsection{Two-Stacks}
The Two-Stacks SWAG algorithm works for \textit{associative} aggregations in scenarios where the sliding window has First-In First-Out (FIFO) semantics --- \textit{i.e.} elements are evicted in the same order they were inserted. Two-Stacks \cite{Tangwongsan-DABA} implements the FIFO queue using two stacks, namely the front stack F and the back stack B. Each element in each of the stacks is a pair \textit{<val, agg>} where \textit{val} is the item's value and \textit{agg} is the aggregation value of everything below it on the stack. The pseudocode for Two-Stacks can be seen in Algorithm \ref{pseudo:2-stacks}, with $\oplus$ as the \textit{combine} function and $\overline{\theta}$ as the identity value of the \textit{combine} function, such that $\overline{\theta} \oplus x$ = $x \oplus \overline{\theta}$ = x. For example, if $\oplus$ is the arithmetic sum then $\overline{\theta}$ is 0. If $\oplus$ is the arithmetic multiplication then $\overline{\theta}$ is 1.

@@

        \Function{insert}{B, v}
            \State{B.push( (v, getStackAggregationValue(B) $\oplus$ v) )}
        \EndFunction

@@

            \If{F.isEmpty()} \Comment{// Flip B onto F and update top aggregation value}
                \While {\textbf{not} B.isEmpty()}
                    \State{F.push(B.top().val, B.top().val $\oplus$ getStackAggregationValue(F))}
                    \State{B.pop()}
                \EndWhile
            \EndIf
            \State{F.pop()}
        \EndFunction
    \end{algorithmic}
\end{algorithm}

@@

\begin{figure}[!htb]
    \begin{center}
      \includegraphics[scale=0.6]{figures/hll-ds.png}
      \caption[HyperLogLog initial state]{HyperLogLog with \textit{m}=4 observable buckets}
      \label{fig:hll-ds}
    \end{center}
\end{figure}

@@

\begin{figure}[!htb]
    \begin{center}
      \includegraphics[scale=1]{figures/hll-insertion.png}
      \caption[HyperLogLog insertion]{HyperLogLog \textit{el} insertion with \textit{m}=4 and \textit{n}=2 bits}
      \label{fig:hll-insert}
    \end{center}
\end{figure}

@@

>>>>

\subsection{Two-Stacks}
The Two-Stacks SWAG algorithm works for \textit{associative} aggregations (recall Table \ref{tbl:aggregations-properties}) in scenarios where the sliding window has First-In First-Out (FIFO) semantics --- \textit{i.e.} elements are evicted in the same order they were inserted. Two-Stacks \cite{Tangwongsan-DABA} implements the FIFO queue using two stacks, namely the front stack F and the back stack B. Each element in each of the stacks is a pair \textit{<val, agg>} where \textit{val} is the item's value and \textit{agg} is the aggregation value of everything below it on the stack. The pseudocode for Two-Stacks can be seen in Algorithm \ref{pseudo:2-stacks}, with $\oplus$ as the \textit{combine} function and $\overline{\theta}$ as the identity value of the \textit{combine} function, such that $\overline{\theta} \oplus x$ = $x \oplus \overline{\theta}$ = x. For example, if $\oplus$ is the arithmetic sum then $\overline{\theta}$ is 0. If $\oplus$ is the arithmetic multiplication then $\overline{\theta}$ is 1.

@@

        \Function{insert}{B, v}
            \State{B.push( \{val: v, agg: getStackAggregationValue(B) $\oplus$ v\} }
        \EndFunction

@@

            \If{F.isEmpty()} \Comment{// Flip B onto F and update top aggregation value}
                \While {\textbf{not} B.isEmpty()}
                    \State{F.push( \{val: B.top().val, agg: B.top().val $\oplus$ getStackAggregationValue(F) \})}
                    \State{B.pop()}
                \EndWhile
            \EndIf
            \State{F.pop()}
        \EndFunction
    \end{algorithmic}
\end{algorithm}

@@

\begin{figure}[!htb]
    \begin{center}
       \hspace{0.5in}
      \includegraphics[scale=0.6]{figures/hll-ds.png}
      \caption[HyperLogLog initial state]{HyperLogLog with \textit{m}=4 observable buckets}
      \label{fig:hll-ds}
    \end{center}
\end{figure}

@@

\begin{figure}[!htb]
    \begin{center}
      \includegraphics[scale=0.8]{figures/hll-insertion.png}
      \caption[HyperLogLog insertion]{HyperLogLog \textit{el} insertion with \textit{m}=4 and \textit{n}=2 bits}
      \label{fig:hll-insert}
    \end{center}
\end{figure}

@@

\textcolor{red}{TODO Find and add versions of Sliding Bloom Filter and Sliding CMS}
